---
title: "Neural Network using the R Neuralnet Package"
output: html_document
---
Packages Needed for this project:
```{r}
library(neuralnet)
library(caret)
library(tidyverse)
```
Create a Data Frame

We're going to create a new variable called mpg2.  If the car has greater than 22 mpg then it's a one else less than 0.  This creates a binary variable, which we can use in the NN.

```{r}
hist(mtcars$mpg)
mtcars$mpg2 <- ifelse(mtcars$mpg > 22,1,0)
data <- mtcars[,2:12]
rows <- sample(nrow(data), nrow(data) * .75, replace = T)
train <- data[rows,]
test <- data[-rows,]
```

We are going to use all the variables.  A '.' signifies all the variables in the data frame.  This helps time wise since you don't have to spell out all the columns.  It is also a logistic neural net model.

```{r}
model <- neuralnet(mpg2 ~ ., train, hidden = 3,
                  act.fct = "logistic", linear.output = F )
?neuralnet
```



```{r}
plot(model)
```





```{r}
predict <- neuralnet::compute(model, test)
predict
```

```{r}
results <- ifelse(predict$net.result > .5, 1,0)

table(results, test$mpg2)
```

